Work Stress

### 2023-03-15 outputs/paper/paper.qmd
Update paper to include Work Hours of a Work Shift & Weekly Schedule under Discussion

## Economic and Policy Factors {#sec-second-point}

In @fig-4, we show other economic factors that might have negatively affected the birth rate in the post-2007 recession across the states. Although the graphs show their inverse relationship, no dramatic change is shown. For instance, as there were somewhere around \$1000 to \$2000 increases in childcare expenses over the past 13 years, we see that the decrease in the actual birth rate is only between 0 to -10. Change in per capita student loans also has increased between \$2500 to \$3250, but it only contributed to the decrease somewhere between 0 to -5 across the states. Based on these findings, it is hard to find an explanation of the dramatic decline in the birth rate since 2007 from economic factors.

>>>>

## Work Hours of a Work Shift & Weekly Schedule

Right now most professionalists are working 40 hours a week, 8 hours shift each day. There is a plan of increasing work hours to 10 hours shift, and work only 4 days each week. But, based on some data, it is definitely not recommended to increase work hours because currently lots of people are always facing work stress when the number of hours are higher. So, if the work shift gets extended longer to reduce the total number of work days, this may cause more work stress because lots of people will be stress over number of tasks to complete during work. Other alternatives that can be used to reduce work stress can be reducing the total number of hours per week from 40 hours to 35 hours. This will allow people to face less work stess because it will reduce the number of hours for them working, and we believe 7 hours work shift can be enough to complete important tasks in a job.
